Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-07 ms_pre_post.Rmd
Further comments, again

<!--- I don't understand the contrast between the two comments, the first of which suggests that the empirical examples of costs cited are not needed here, and the second of which suggests that we need to be more explicit about why we did things the way we did. Hence, I have revised to clarify that we made the modelling choices that we did with respect to costs *because they are observed in empirical systems*. Of course, the costs that we modelled are not the *only* kinds of 'costs' that are observed in empirical systems (hence the Roberts reference), so other models might want to look into different types of costs. I agree that it would not be at all surprising if a reviewer raised a question about how we modelled the costs (or anything else), but this always seems to be true for modelling and I think it kind of misses the big picture about how models like this try to develop theory. We can't model *every* kind of cost that we can possibly think of, and we're not modelling a specific system where we might be able to justify some costs being more reasonable than others. We also can't (I don't think) logically show with an IBM that the type of cost will be arbitray with respect to the questions of interest (i.e., any cost will do). In the end, we have to make reasonable decisions about how to model costs and work from there. I think that citing empirical studies shows that our assumptions of cost type are reasonable for some systems (though potentially not others). Had we made different assumptions, I suspect we'd get queries from some readers wondering why we didn't do it a different way. --->

>>>>

<!--- I don't understand the contrast between the two comments, the first of which suggests that the empirical examples of costs cited are not needed here, and the second of which suggests that we need to be more explicit about why we did things the way we did. Hence, I have revised to clarify that we made the modelling choices that we did with respect to costs *because they are observed in empirical systems*. Of course, the costs that we modelled are not the *only* kinds of 'costs' that are observed in empirical systems (hence the Roberts reference), so other models might want to look into different types of costs. I agree that it would not be at all surprising if a reviewer raised a question about how we modelled the costs (or anything else), but this always seems to be true for modelling and I think it kind of misses the big picture about how models like this try to develop theory. We can't model *every* kind of cost that we can possibly think of (nor would we want to), and we're not modelling a specific system where we might be able to justify some costs being more reasonable than others. We also can't (I don't think) logically show with an IBM that the type of cost will be arbitray with respect to the questions of interest (i.e., any cost will do). In the end, we have to make reasonable decisions about how to model costs and work from there. I think that citing empirical studies shows that our assumptions of cost type are reasonable for some systems (though potentially not others). Had we made different assumptions, I suspect we'd get queries from some readers wondering why we didn't do it a different way. I don't mean to keep belabouring this point, but I think that the point of using a model to develop theory isn't to match your assumptions with empirical reality as closely as possible (if we tried, we'd miss a lot of important stuff!). Assumptions need to be clear and useful for addressing the theoretical question(s) of interest -- when I review theory papers, this is the criteria I have in mind, not (necessarily) whether or not the assumptions match how things are in nature (they might deliberately not be, for the better!). The only reason I have repeatedly justified the cost assumption is, really, for fear that readers might not entirely understand the nature of model assumptions in theory. --->
